---
title: "plots examples"
output: 
  html_document:
    toc: true
    toc_float: true
---
```{r}
library(tidyverse)
library(ggridges)
library(p8105.datasets)
```

Import the weather data
```{r}
data("weather_df")
```

Making our first plot :)
```{r}
ggplot(weather_df, mapping = aes(x = tmin, y = tmax))
```

A blanking one, That’s because I’ve defined the data and the aesthetic mappings, but haven’t added any geoms: ggplot knows what data I want to plot and how I want to map variables, but not what I want to show. Below I add a geom to define my first scatterplot.

Add geom_point()

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()
```

if you want to have some pre-processing

```{r}
weather_df |>
  ggplot(aes(x = tmin, y = tmax)) + 
  geom_point()
```

We assign it to a variable
```{r}
ggp_weather = 
  weather_df |>
  ggplot(aes(x = tmin, y = tmax)) 

ggp_weather + geom_point()
```

We get a warning about missing value. We want to check the rows that are missing.
nariar?
```{r}
weather_df |>
  filter(is.na(tmax))
```


## Advanced and Fancier scatterplots

incorporate name with different color
```{r}
weather_df |>
  ggplot(aes(x = tmin, y = tmax, colour = name)) +
  geom_point()
# geom_point(alpha = 0.3) This can show some density, it makes the color lighter
```

```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name))
```